### 2020-09-15 serial_analysis.tex
update

% Created by tikzDevice version 0.12.3 on 2020-04-30 02:40:57
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (650.43,216.81);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (216.81,216.81);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (216.81,216.81);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 34.64, 30.69) rectangle (211.31,194.15);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (100.89,194.15) --
	(106.42,189.20) --
	(111.94,184.25) --
	(117.46,179.29) --
	(122.98,174.34) --
	(128.50,169.39) --
	(134.02,164.43) --
	(139.54,159.48) --
	(145.06,154.52) --
	(150.58,149.57) --
	(156.10,144.62) --
	(161.62,139.66) --
	(167.14,134.71) --
	(172.66,129.76) --
	(178.19,124.80) --
	(183.71,119.85) --
	(189.23,114.90) --
	(194.75,109.94) --
	(200.27,104.99) --
	(205.79,100.04) --
	(211.31, 95.08);
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 34.64,104.99) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 45.69,161.34) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 51.21,136.36) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 56.73,144.62) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 62.25,144.62) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 67.77,164.43) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.29,164.43) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 78.81,144.62) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.33,159.48) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.85,137.19) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 95.37,120.06) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (100.89,120.16) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.42,124.02) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.94,113.45) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.46,121.02) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.98,112.94) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.50,109.78) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.02,113.37) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.54,101.81) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.06,105.30) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (150.58, 99.53) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.10, 97.67) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.62, 97.70) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.14, 92.46) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.66, 89.55) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.19, 95.98) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.71, 94.09) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (189.23, 85.17) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (200.27, 70.31) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (211.31, 60.41) circle (  1.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.64,104.99) --
	( 34.64,104.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.64,104.99) --
	( 34.64,104.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.64,104.99) --
	( 34.64,104.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 45.69,173.47) --
	( 45.69,173.47);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 45.69,173.47) --
	( 45.69,142.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 45.69,142.26) --
	( 45.69,142.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.21,167.16) --
	( 51.21,167.16);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.21,167.16) --
	( 51.21,115.39);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.21,115.39) --
	( 51.21,115.39);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.73,154.03) --
	( 56.73,154.03);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.73,154.03) --
	( 56.73,135.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.73,135.21) --
	( 56.73,135.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.25,173.35) --
	( 62.25,173.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.25,173.35) --
	( 62.25,107.47);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.25,107.47) --
	( 62.25,107.47);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 67.77,164.43) --
	( 67.77,164.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 67.77,164.43) --
	( 67.77,164.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 67.77,164.43) --
	( 67.77,164.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.29,187.96) --
	( 73.29,187.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.29,187.96) --
	( 73.29,140.90);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.29,140.90) --
	( 73.29,140.90);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.81,154.03) --
	( 78.81,154.03);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.81,154.03) --
	( 78.81,135.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.81,135.21) --
	( 78.81,135.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 84.33,159.48) --
	( 84.33,159.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 84.33,159.48) --
	( 84.33,159.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 84.33,159.48) --
	( 84.33,159.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.85,158.36) --
	( 89.85,158.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.85,158.36) --
	( 89.85,120.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.85,120.22) --
	( 89.85,120.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.37,168.89) --
	( 95.37,168.89);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.37,168.89) --
	( 95.37, 85.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.37, 85.67) --
	( 95.37, 85.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.89,157.00) --
	(100.89,157.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.89,157.00) --
	(100.89, 96.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.89, 96.94) --
	(100.89, 96.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (106.42,147.34) --
	(106.42,147.34);

\path[draw=drawColor,line width= 0.6pt,line join=round] (106.42,147.34) --
	(106.42, 94.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (106.42, 94.59) --
	(106.42, 94.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (111.94,156.63) --
	(111.94,156.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] (111.94,156.63) --
	(111.94, 85.17);

\path[draw=drawColor,line width= 0.6pt,line join=round] (111.94, 85.17) --
	(111.94, 85.17);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.46,164.43) --
	(117.46,164.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.46,164.43) --
	(117.46, 94.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.46, 94.22) --
	(117.46, 94.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] (122.98,163.56) --
	(122.98,163.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (122.98,163.56) --
	(122.98, 72.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (122.98, 72.91) --
	(122.98, 72.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (128.50,142.39) --
	(128.50,142.39);

\path[draw=drawColor,line width= 0.6pt,line join=round] (128.50,142.39) --
	(128.50, 85.17);

\path[draw=drawColor,line width= 0.6pt,line join=round] (128.50, 85.17) --
	(128.50, 85.17);

\path[draw=drawColor,line width= 0.6pt,line join=round] (134.02,141.52) --
	(134.02,141.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] (134.02,141.52) --
	(134.02, 90.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (134.02, 90.13) --
	(134.02, 90.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.54,125.30) --
	(139.54,125.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.54,125.30) --
	(139.54, 70.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.54, 70.07) --
	(139.54, 70.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (145.06,143.75) --
	(145.06,143.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (145.06,143.75) --
	(145.06, 65.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (145.06, 65.36) --
	(145.06, 65.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (150.58,135.45) --
	(150.58,135.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] (150.58,135.45) --
	(150.58, 70.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (150.58, 70.07) --
	(150.58, 70.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (156.10,129.26) --
	(156.10,129.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (156.10,129.26) --
	(156.10, 40.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (156.10, 40.59) --
	(156.10, 40.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.62,125.79) --
	(161.62,125.79);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.62,125.79) --
	(161.62, 58.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.62, 58.43) --
	(161.62, 58.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (167.14,109.94) --
	(167.14,109.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (167.14,109.94) --
	(167.14, 64.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] (167.14, 64.37) --
	(167.14, 64.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] (172.66,107.96) --
	(172.66,107.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (172.66,107.96) --
	(172.66, 73.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (172.66, 73.29) --
	(172.66, 73.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (178.19,109.94) --
	(178.19,109.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (178.19,109.94) --
	(178.19, 77.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (178.19, 77.74) --
	(178.19, 77.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (183.71,100.04) --
	(183.71,100.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (183.71,100.04) --
	(183.71, 85.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (183.71, 85.67) --
	(183.71, 85.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (189.23, 85.17) --
	(189.23, 85.17);

\path[draw=drawColor,line width= 0.6pt,line join=round] (189.23, 85.17) --
	(189.23, 85.17);

\path[draw=drawColor,line width= 0.6pt,line join=round] (189.23, 85.17) --
	(189.23, 85.17);

\path[draw=drawColor,line width= 0.6pt,line join=round] (200.27, 70.31) --
	(200.27, 70.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] (200.27, 70.31) --
	(200.27, 70.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] (200.27, 70.31) --
	(200.27, 70.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] (211.31, 83.94) --
	(211.31, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (211.31, 83.94) --
	(211.31, 36.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (211.31, 36.88) --
	(211.31, 36.88);

>>>>

% Created by tikzDevice version 0.12.3 on 2020-09-14 16:14:30
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (1156.32,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 31.71, 30.69) rectangle (283.58,266.42);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.71, 30.69) rectangle (283.58,266.42);
\definecolor{fillColor}{gray}{0.35}

\path[fill=fillColor] ( 31.71, 30.69) rectangle ( 38.40, 34.10);

\path[fill=fillColor] ( 46.57, 30.69) rectangle ( 53.26, 37.52);

\path[fill=fillColor] ( 54.00, 30.69) rectangle ( 60.69, 40.94);

\path[fill=fillColor] ( 61.43, 30.69) rectangle ( 68.12, 37.52);

\path[fill=fillColor] ( 68.86, 30.69) rectangle ( 75.55, 40.94);

\path[fill=fillColor] ( 76.29, 30.69) rectangle ( 82.98, 34.10);

\path[fill=fillColor] ( 83.72, 30.69) rectangle ( 90.41, 37.52);

\path[fill=fillColor] ( 91.15, 30.69) rectangle ( 97.84, 40.94);

\path[fill=fillColor] ( 98.58, 30.69) rectangle (105.27, 37.52);

\path[fill=fillColor] (106.01, 30.69) rectangle (112.70, 44.35);

\path[fill=fillColor] (113.44, 30.69) rectangle (120.13, 85.35);

\path[fill=fillColor] (120.87, 30.69) rectangle (127.56, 85.35);

\path[fill=fillColor] (128.30, 30.69) rectangle (134.99, 92.18);

\path[fill=fillColor] (135.73, 30.69) rectangle (142.42, 95.60);

\path[fill=fillColor] (143.16, 30.69) rectangle (149.84,150.26);

\path[fill=fillColor] (150.59, 30.69) rectangle (157.27,194.68);

\path[fill=fillColor] (158.02, 30.69) rectangle (164.70,204.93);

\path[fill=fillColor] (165.45, 30.69) rectangle (172.13,198.09);

\path[fill=fillColor] (172.88, 30.69) rectangle (179.56,218.59);

\path[fill=fillColor] (180.31, 30.69) rectangle (186.99,245.92);

\path[fill=fillColor] (187.74, 30.69) rectangle (194.42,256.17);

\path[fill=fillColor] (195.17, 30.69) rectangle (201.85,198.09);

\path[fill=fillColor] (202.60, 30.69) rectangle (209.28,187.84);

\path[fill=fillColor] (210.03, 30.69) rectangle (216.71,191.26);

\path[fill=fillColor] (217.46, 30.69) rectangle (224.14,177.59);

\path[fill=fillColor] (224.89, 30.69) rectangle (231.57,136.60);

\path[fill=fillColor] (232.31, 30.69) rectangle (239.00,116.10);

\path[fill=fillColor] (239.74, 30.69) rectangle (246.43,102.43);

\path[fill=fillColor] (247.17, 30.69) rectangle (253.86, 75.10);

\path[fill=fillColor] (254.60, 30.69) rectangle (261.29, 61.43);

\path[fill=fillColor] (262.03, 30.69) rectangle (268.72, 51.18);

\path[fill=fillColor] (269.46, 30.69) rectangle (276.15, 37.52);

\path[fill=fillColor] (276.89, 30.69) rectangle (283.58, 34.10);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.71, 30.69) rectangle (283.58,266.42);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76, 27.66) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76, 95.98) {20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76,164.31) {40};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76,232.64) {60};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96, 30.69) --
	( 31.71, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96, 99.02) --
	( 31.71, 99.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,167.34) --
	( 31.71,167.34);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,235.67) --
	( 31.71,235.67);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 79.63, 27.94) --
	( 79.63, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (131.64, 27.94) --
	(131.64, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (183.65, 27.94) --
	(183.65, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (235.66, 27.94) --
	(235.66, 30.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 79.63, 19.68) {Jan 13};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (131.64, 19.68) {Jan 20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (183.65, 19.68) {Jan 27};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (235.66, 19.68) {Feb 03};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (157.65,  7.64) {Symptom onset date};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,148.55) {Number of cases with a known infector/infectee pair};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 31.71,274.49) {A. Epidemic curve};
\end{scope}
\begin{scope}
\path[clip] (299.25,  0.00) rectangle (567.99,289.08);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (299.25,  0.00) rectangle (567.99,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (333.90, 30.69) rectangle (562.49,266.42);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate=-45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (499.08,195.87) {maximum observable};

\node[text=drawColor,rotate=-45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (384.78, 74.43) {minimum observable};

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (419.62,266.42) --
	(426.76,259.28) --
	(433.91,252.14) --
	(441.05,244.99) --
	(448.19,237.85) --
	(455.34,230.71) --
	(462.48,223.56) --
	(469.62,216.42) --
	(476.77,209.27) --
	(483.91,202.13) --
	(491.05,194.99) --
	(498.20,187.84) --
	(505.34,180.70) --
	(512.48,173.56) --
	(519.63,166.41) --
	(526.77,159.27) --
	(533.91,152.13) --
	(541.06,144.98) --
	(548.20,137.84) --
	(555.35,130.70) --
	(562.49,123.55);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (333.90,116.41) --
	(341.04,109.26) --
	(348.18,102.12) --
	(355.33, 94.98) --
	(362.47, 87.83) --
	(369.61, 80.69) --
	(376.76, 73.55) --
	(383.90, 66.40) --
	(391.04, 59.26) --
	(398.19, 52.12) --
	(405.33, 44.97) --
	(412.47, 37.83) --
	(419.62, 30.69);
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (333.90,137.84) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (348.18,219.10) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (355.33,183.08) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (362.47,194.99) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.61,194.99) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (376.76,223.56) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (383.90,223.56) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (391.04,194.99) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (398.19,216.42) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (405.33,184.27) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (412.47,159.58) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (419.62,159.72) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (426.76,165.29) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (433.91,150.04) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (441.05,160.95) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (448.19,149.30) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (455.34,144.74) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (462.48,149.93) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (469.62,133.26) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (476.77,138.29) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (483.91,129.96) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (491.05,127.28) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (498.20,127.33) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (505.34,119.77) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (512.48,115.57) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (519.63,124.85) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (526.77,122.12) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (533.91,109.26) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (548.20, 87.83) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (562.49, 73.55) circle (  1.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (333.90,137.84) --
	(333.90,137.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (333.90,137.84) --
	(333.90,137.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (333.90,137.84) --
	(333.90,137.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (348.18,236.60) --
	(348.18,236.60);

\path[draw=drawColor,line width= 0.6pt,line join=round] (348.18,236.60) --
	(348.18,191.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (348.18,191.59) --
	(348.18,191.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (355.33,227.49) --
	(355.33,227.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (355.33,227.49) --
	(355.33,152.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (355.33,152.84) --
	(355.33,152.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (362.47,208.56) --
	(362.47,208.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (362.47,208.56) --
	(362.47,181.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (362.47,181.41) --
	(362.47,181.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (369.61,236.42) --
	(369.61,236.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (369.61,236.42) --
	(369.61,141.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (369.61,141.41) --
	(369.61,141.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (376.76,223.56) --
	(376.76,223.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (376.76,223.56) --
	(376.76,223.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (376.76,223.56) --
	(376.76,223.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (383.90,257.49) --
	(383.90,257.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (383.90,257.49) --
	(383.90,189.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] (383.90,189.63) --
	(383.90,189.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] (391.04,208.56) --
	(391.04,208.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (391.04,208.56) --
	(391.04,181.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (391.04,181.41) --
	(391.04,181.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (398.19,216.42) --
	(398.19,216.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (398.19,216.42) --
	(398.19,216.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (398.19,216.42) --
	(398.19,216.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (405.33,214.81) --
	(405.33,214.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (405.33,214.81) --
	(405.33,159.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (405.33,159.81) --
	(405.33,159.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (412.47,229.99) --
	(412.47,229.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] (412.47,229.99) --
	(412.47,109.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (412.47,109.98) --
	(412.47,109.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (419.62,212.85) --
	(419.62,212.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (419.62,212.85) --
	(419.62,126.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (419.62,126.23) --
	(419.62,126.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (426.76,198.92) --
	(426.76,198.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] (426.76,198.92) --
	(426.76,122.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (426.76,122.84) --
	(426.76,122.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (433.91,212.31) --
	(433.91,212.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] (433.91,212.31) --
	(433.91,109.26);
